---
title: "Homework 1"
author: "Michael Whelan"
format: pdf
editor: visual
toc: true
---

\newpage

## 1. Intro

For this assignment I will be looking at the `women` data which is a built in dataset in R. This dataset records the average:

-   Heights
-   Weights

Of women in America between the ages of 30-39. These are also the **variables** for this dataset.

We will now load and inspect the first 6 lines of the data  data

```{r, echo=FALSE}
# Load data
data(women)

# Print data
head(women)
```

\

We can see get the average height for this dataset using the following formula:

$$
\bar{x} = \frac{1}{n}\sum_{i=1}^n{x_{i}}
$$ 

The average height is: `r mean(women$height)`

We will also find the average weight for this dataset using the same formula above

The average weight is: `r mean(women$weight)`

## 2. Plot

Now we will plot this data. We can use the packages `ggplot2` for this. After loading it we can create our plot.

```{r, echo = F}
library(ggplot2)
```

\

```{r, echo = F, message=FALSE}
# Create the scatter plot with linear regression line and add legends
p1 <- ggplot(women, aes(x = height, y = weight)) +
  geom_point(aes(color = "Data Points"), size = 3) +
  geom_smooth(aes(color = "Regression Line"), method = "lm", se = FALSE) +
  scale_color_manual(name = " ", values = c("Data Points" = "blue", "Regression Line" = "red")) +
  labs(title = "Height vs Weight with Linear Regression", x = "Height (inches)", y = "Weight (lbs)") +
  theme(plot.title = element_text(hjust = 0.5))

# Display the plot
print(p1)

```

Looking at the plot there is a linear relationship between the `height` and `weight` of women in this dataset. It looks like as height increases weight also increases indicating a strong positive linear relationship.

I have also constructed a regression line for this plot. It is clear the regression line predicts the data very well.

------------------------------------------------------------------------
